FTLR proof cases

### 2018-05-24 fully-abstract-comp/ftlr-proof-cases.tex
The new cases to the FTLR proof.

>>>>

By the above observation, we know that $\Phi_S \step[\gc] \Phi_S'$ and $\Phi_T \step
\Phi_T'$ for some $\Phi_S'$ and $\Phi_T'$. According to
Lemma~\ref{lem:lro-anti-red-gen}, it suffices to show:
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
Consider each of the possible cases:

In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
either assume that the target configuration terminates or that the source
configuration terminates, but in either case it leads to a contradiction with
the failing configuration.

In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to get
\[
  \npair[n'-1]{(((\perm,\lin),\baddr,\eaddr,\aaddr+1),((\perm,\lin),\baddr,\eaddr,\aaddr+1))} \in \lre(W)
\]
This is possible by using the initial assumptions along with Lemma \ref{lem:check-stack-addr-before-call-dc}, \ref{lem:use-return-seals-call-dc}, \ref{lem:handle-trusted-seals-prop-dc}, \ref{lem:never-store-seal-code-cap-dc}, and \ref{lem:downwards-closed}.
By Lemma~\ref{lem:downwards-closed}, we know $\memSat[n'-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.
By Lemma~\ref{lem:downwards-closed} and the fact that integers are always safe,
we know $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$.
This allows us to conclude
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
as desired.
